Acceleration of Derivative Calculations with Application to Radial Basis Function -- Finite-Differences on the Intel MIC Architecture

### 2013-10-19 ieee_paper.tex
ccl

In a future work, we will examine the effect of larger stencil sizes, double precision and port common techniques from SpMV. We will also integrate the techniques
presented in this paper within a fluid simulation using RBF-FD.

>>>>

In a future work, we will examine the effect of larger stencil sizes,
double precision. The presented performance do not reach the predicted
peak and we believe that common techniques from SpMV such as cache
partitioning can be successfully applied. We will also integrate the
techniques presented in this paper within a fluid simulation using
RBF-FD.
